\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}

% Custom section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Global list formatting
\setlist[itemize]{leftmargin=1.5cm, labelsep=0.4cm, noitemsep, topsep=2pt}

\begin{document}
\pagestyle{empty}

% Header
\begin{center}
    {\Huge \scshape Delfin Eryılmaz} \\[2mm]
    \footnotesize
    {\faMapMarker\ Ankara, Türkiye} ~
    {\faPhone\ +90 (533) 816 0616} ~
    {\faEnvelope\ \href{mailto:delfin.eryilmaz@ug.bilkent.edu.tr}{delfin.eryilmaz@ug.bilkent.edu.tr}} ~
    {\faLinkedin\ \href{https://www.linkedin.com/in/delfin-eryilmaz-49659b369/}{LinkedIn}} ~
    {\faGithub\ \href{https://github.com/DelfinEryilmaz}{GitHub}}
    \vspace{-8pt}
\end{center}

% Education
\section{EDUCATION}
\noindent \textbf{Bilkent University} \hfill Sep 2024 -- Jan 2029 (Expected) \\
\textit{B.S. in Computer Science}
\begin{itemize}
    \item[\textbullet] \textbf{GPA: 3.86 / 4.00}
    \item[\textbullet] \textbf{Relevant Coursework:} Calculus I–II, Algorithms and Programming I–II (Java), Data Structures (C++), Digital Design (SystemVerilog), Discrete Mathematics, Physics II (E\&M), English \& Composition I–II.
\end{itemize}

\vspace{5pt}
\noindent \textbf{TOBB Bülent Koşmaz Fen Lisesi} \hfill Sep 2023 -- Jun 2024 \\
\textit{High School Diploma}
\begin{itemize}
    \item[\textbullet] \textbf{Honors:} Graduated as \textbf{Salutatorian} (GPA: 98.7 / 100).
\end{itemize}

% Technical Skills
\section{TECHNICAL SKILLS}
\begin{itemize}
    \item[\textbullet] \textbf{Programming:} Java (Advanced), Python, C++, JavaScript, SQL, SystemVerilog (Vivado).
    \item[\textbullet] \textbf{Frameworks \& Libraries:} JavaFX, WebSockets, Node.js, PostgreSQL, Git.
    \item[\textbullet] \textbf{Cloud \& Systems:} Google Cloud Platform, Client–Server Architecture, REST/WebSocket-based Communication.
\end{itemize}

% Languages
\section{LANGUAGES}
\begin{itemize}
    \item[\textbullet] Turkish (Native), English (Fluent), German (Introductory).
\end{itemize}

% Projects
\section{PROJECTS}
\vspace{5pt}
\noindent \textbf{Studium} \,|\, \textit{\href{https://github.com/boylebirkisi/CS102-Studium-App-Group-Project}{Source Code}}
\hfill \textit{JavaFX | WebSockets | PostgreSQL | Google Cloud}
\begin{itemize}
    \item[\textbullet] \textbf{Collaborative System:} Built a real-time \textbf{study-management desktop application} using a \textbf{client–server architecture}, enabling synchronized multi-user interaction.
    \item[\textbullet] \textbf{Networking \& Backend:} Implemented \textbf{bidirectional WebSocket communication} for real-time synchronization of user actions and messages; deployed backend services on \textbf{Google Cloud}.
    \item[\textbullet] \textbf{Frontend \& Teamwork:} Designed an interactive \textbf{JavaFX user interface} with modular components and collaborated in a \textbf{Git-based team environment}.
\end{itemize}

% Extracurricular
\section{EXTRACURRICULAR}
\noindent \textbf{GazeteBilkent} \hfill Nov 2025 -- Present \\
\textit{Writer} \,|\, \textit{\href{https://gazetebilkent.com/author/delfineryilmaz/}{Profile}}
\begin{itemize}
    \item[\textbullet] Cultivating analytical thinking and intellectual versatility through research and writing on art, culture, and philosophy, translating complex ideas for a broad academic audience.
\end{itemize}

% Achievements
\section{ACHIEVEMENTS}
\begin{itemize}
    \item[\textbullet] \textbf{Dean’s High Honor List:} Recognized for outstanding academic performance (2024–2025).
    \item[\textbullet] \textbf{YKS National Ranking:} Ranked \textbf{2237th} among 3+ million students.
\end{itemize}

\end{document}
